Microplatforms: Product platforms as code

### 2018-05-31 paper.tex
Add GitOps

GitOps

@@

With microservice orchestration and policy being captured as code, the question arises as to whether or not to share microservice instances between application stacks. In other words, can each application have its own replica of the same microservice or should there be a shared instance? Notice this choice is only valid for stateless microservices, as when replicating microservices which hold state, data replication and distributed transaction concerns arise, which are typically hard enough to solve to warrant being solved once and only once. This difficulty should not be underestimated and it is often a good approach to try to split the microservice into its business logic and persistent data storage concerns and separate out as much of the stateless part of as possible, e.g. by using a Database as a Service (DbaaS). The business logic then becomes a separate, now stateless, microservice.

>>>>

Service orchestration as code also enables a practice that has become known as GitOps, which advocates performing operations in a runtime environment through changes to a version control repository. In practice, it can mean a cluster has an associated git repository holding all the service orchestration configuration for every single application running in it. In order to deploy an application, a CI service pushes a new revision into this repository and the cluster (more precisely a service running within it) responds to the event by pulling the configuration and attempting to deploy it. This serves as an inversion of control mechanism, removing the need for a CI service (typically in a non-production environment) to have direct access to and control over clusters in a production environment, and also allows for final checks to be performed by the cluster itself to decide whether to accept the deployment. As a side-effect, the state of the cluster is fully audited over time and can be restored in a different cluster even months later. Optionally, this also means no outside access to deployment APIs is needed for the production clusters, increasing security.

@@

With microservice orchestration and policy being captured as code, the question arises as to whether or not to share microservice instances between application stacks. In other words, can each application have its own replica of the same microservice or should there still be a shared instance? Notice this choice is only valid for stateless microservices, as when replicating microservices which hold state, data replication and distributed transaction concerns arise, which are typically hard enough to solve to warrant being solved once and only once. This difficulty should not be underestimated and it is often a good approach to try to split the microservice into its business logic and persistent data storage concerns and separate out as much of the stateless part of as possible, e.g. by using a Database as a Service (DbaaS). The business logic then becomes a separate, now stateless, microservice.
